\papertitle

### 2014-03-20 final-report/paper.tex
Rewrote abstract

We propose a visualization system to explore and understand query
execution and data movement in a distributed database management system
(DDBMS). Our tool provides insight into: (1) data flow between query segments
and between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization. Our tool, \system, helps
developers understand and improve query execution, and provides insight into
common problems such as data skew or performance bottlenecks.

@@

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues,
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool,
\system, uses profiling logs from \emph{Myria} \cite{myria} as the prototype DDMS. Myria is a distributed
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently, Myria does not offer a visualization tool designed to show the physical query plan, job execution and network
communication between distributed workers. \system allows the programmer/database administrator to visualize the following aspects
of query execution.

@@

\todo{it's not a dag, as we noticed}

>>>>

We propose \system, a visualization tool that helps database developers/users
explore and understand query execution and data movement in a distributed
database management system (DDBMS). \system provides quick insight into common
problems such as data skew or performance bottleneck by leveraging
visualization techniques to present: (1) data flow between query segments and
between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization.

@@

Our goal is to build a visualization tool designed to help a database administrator understand the data flow and run-time
performance during query execution in a Distributed Database Management System (DDBMS). Using our tool, the
database programmer or administrator could quickly discover run-time bottlenecks as well as problematic data skew issues,
saving them significant guesswork and programming effort to identify the appropriate logs to analyze. Our visualization tool,
\system, uses profiling logs from \emph{Myria} \cite{myria} as the prototype DDMS. Myria is a distributed
database platform that provides \emph{big data management and analytics as a service} primarily for scientific applications.
Myria takes queries in high-level query languages, such as SQL, translating them into physical query plans and finally executing
them in parallel. Currently, Myria does not offer a visualization tool designed to show the physical query plan, job execution and network
communication between distributed workers. \system allows the programmer/database administrator to visualize the following aspects
of query execution.
\todo{it's not a dag, as we noticed}

@@
